Sketch Recognition using Particle Swarm Optimization Algorithm

### 2009-04-22 trunk/draft/Results.tex
aftetr my change

\chapter{Evaluation}
\label{sec:Evaluation}
This chapter describes and illustrates the experiments performed on the system. In the chapter, section \ref{sec:ExperimentsSetup} describes the experimental setup. Section \ref{sec:Datasets} describes the datasets used. Section \ref{sec:ResultsDetails} demonstrates and analyzes the results.

The system has two main parts the DPSO stroke segmentation and symbol recognition. Each part is evaluated separately. The preprocessing procedures and computation is evaluated using their effect on the segmentation algorithm. These results are reported in section \ref{sec:ResultsDetails}. The effect of number of agents, the error thresholds and various other PSO parameters are investigated in Section \ref{sec:PSO}. %The results presented in Section \ref{sec:ResultsDetails} and \ref{sec:PSO}.

The recognition system evaluation is presented in Section \ref{sec:SegmentationAlgorithms}. The recognition rate (computed as the number of correctly recognized samples divided by the total number of samples in the test) for each segmentation algorithm compared to another segmentation algorithm are reported in \ref{sec:recognitionAlgorithms}. Next, a comparison between different shapes and datasets and it influence on the recognition rate is presented in Section \ref{sec:EffectsofSymbolComplixity}. Finally, a comparison between different feature vectors is reported in Section \ref{sec:featuresComparisions}.

@@

 %We divided the dataset equally into training set and test set.  The results displayed are the recognition accuracy resulted from the classifier after recognizing the symbols. \\
%We divided the dataset into four sets each set contains four different users. Furthermore, each set is divided into train and test set where the trained set where used to train the classifiers and the test set where used for testing.  The algorithms are then tested using the four sets and the results are averaged.
\begin{figure}[]\centering
\fbox{  \parbox{8cm}{% 
		\includegraphics[scale=0.7]{images/symbolSet.eps}	}
		}
	\caption{The Symbol Set}
	\label{fig:symbolSet}
\end{figure}

@@

	\caption{Example of Logic Symbols}
	\label{fig:LogicSet}
\end{figure}
\begin{figure}[]\centering

@@

	\caption{Example of Electrical Symbols}
	\label{fig:ElectSet}
\end{figure}
\begin{table}
\begin{center}
\scalebox{0.9}{
 \begin{tabular}{|p{5cm}|p{2.5cm}|p{2.5cm}|p{2.5cm}|}
 \hline
 & Hs-DB &  EL-DB & LD-DB \\ \hline
No of samples  &  7791 & 2764 & 1859 \\ \hline
No of categories  & 13 & 15 & 8 \\ \hline
Avg. Samples per Category& 600 & 184 & 232 \\\hline 
No of users  & 16 & 7 & 7 \\  \hline
Balanced & Yes&No & No \\ \hline
Splits  & 5 random splits  & 5 random splits  & 5 random splits  \\ \hline
Examples & Figure \ref{fig:symbolSet}  & Figure \ref{fig:ELsymbolSet}  & Figure \ref{fig:LogicsymbolSet}   \\ \hline
\end{tabular}
}
\caption[Datasets Comparisons]{Datasets Comparisons} 
\label{tab:datasets}

@@

	\item [Recognition accuracy] We measure recognition performance for each algorithm by determining the number of correctly identified symbols in the whole dataset. Note that All the results are shown as the average of the four split of the dataset used. 
\end{description}

@@

 The effect of number of agents, the error thresholds and various other parameters was investigated. The result of these tests are shown in Figure \ref{fig:swarmtesting} and \ref{fig:swarmtesting2}. Figure \ref{fig:swarmtesting} shows that as the number of agents increase the \textit{Segmentation Error} value decrease. Similar results for the maximum swarm iterations are shown in Figure \ref{fig:swarmtesting}.  Other algorithm parameters like $c_1$,$c_2$ that were mentioned in Section\ref{sec:ParticleSwarmAlgorithm} are tested using similar tests (Figure \ref{fig:swarmparamterw.jpg} and \ref{fig:swarmtesting2}). The final values are for maximum number of iteration = 80 with 15 particles. The final number of agents and maximum swarm iteration used in the system was based trade off between errors achieved versus the computation time.

 \begin{figure}
	\centering		
	 \includegraphics[scale=0.5]{paperImages/swarmAgentTest.jpg.eps}
	 	\caption{Segmentation Error Vs. Number of agents}
	 	\label{fig:swarmtesting}
	%\caption{Experiments results :} a)    b) c) 
\end{figure}

@@

\begin{figure}
	\centering
		\includegraphics[scale=0.6]{results/LDRes.eps}
	\caption{Result Algorithms on LD-DB}
	\label{fig:LDRes}

\end{figure}
\begin{figure}
	\centering
		\includegraphics[scale=0.6]{results/ElRes.eps}
	\caption{Results of Algorithms on EL-DB}
	\label{fig:ElRes}
\end{figure}

@@

 The effects of symbol complexity in a dataset were testing in the following experiment. These experiments test how many samples will be required to finally obtain good performance from the recognizer system. In the following experiments, we tested the system using different number of sample per category. 
 Figure \ref{fig:Alg1Ds} and \ref{fig:Alg2Ds} shows that Hs-DB requires more number of sample for training to achieve same result as in other data sets. This is due that it contains less signal and conceptual variation that the other two datasets. Figure \ref{fig:samplesofHS-DB.jpg} shows sample of data collected from one user in Hs-Db it is clear that it has reasonable amount of variation between users but it is limited. Recognizing symbols that contains high variation in drawing style using fewer symbols in training prove the efficiency of our system.
 \begin{figure}
	\centering
		\includegraphics{results/Alg1Ds.eps}
	\caption{AlgS1 on different datasets}
	\label{fig:Alg1Ds}
\end{figure}
\begin{figure}
	\centering
		\includegraphics{results/Alg2Ds.eps}
	\caption{AlgS2 on different Datasets }
	\label{fig:Alg2Ds}
\end{figure}

  Figure \ref{} and \ref{} shows examples of correctly recognized symbol using our system. The figure shows that system recognized some hard to recognize example in both EL-DB and DL-DB. An example of symbols that was not correctly recognized are in Figure \ref{}. Most of the wrong classifications were due to how messy the user draw symbols and how similarly they are conceptual. Table \ref{} show the confusion matrix of EL-DB which shows that most error were between capacitor, batter and crystal which differ only on number of parallel lines. Table \ref{tab:ConfusionMatrix} (confusion matrix) shows the types of error in Hs-DB which shows that the system was confused between parallelogram and trapezoid, moon and arch. Those errors were due to users drawing styles as some user may draw a parallelogram as a trapezoid.

\begin{figure}
	\includegraphics[scale=0.5]{results/samplesofHS-DB.jpg.eps}
	\caption{Hs-DB shapes drawn by single user}
	\label{fig:samplesofHS-DB.jpg}
\end{figure}
 \begin{table*}
	\centering
	%\small
%	\scalebox{0.7}{
		%	\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}\hline 
	\scalebox{0.7}{
		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}\hline 
 Categories 	&ellipse	&heart	&trapezoid	&pentagon	&arch	&hexagon	&square	&triangle	&cube	&cylinder	&parallelogram	&moon	&callout\\ \hline
ellipse	&155	&9	&0	&0	&0	&5	&0	&0	&0	&0	&0	&6	&0\\ \hline
heart	&0	&109	&1	&1	&25	&0	&0	&1	&0	&0	&2	&1	&1\\ \hline
trapezoid	&0	&0	&103	&5	&2	&0	&0	&2	&0	&0	&34	&0	&0\\ \hline
pentagon	&0	&0	&20	&121	&0	&20	&6	&2	&0	&0	&1	&0	&0\\ \hline
arch	&0	&1	&13	&0	&86	&0	&0	&2	&3	&0	&2	&0	&0\\ \hline
hexagon	&0	&0	&0	&0	&0	&98	&0	&0	&0	&0	&0	&0	&0\\ \hline
square	&0	&0	&1	&0	&2	&0	&107	&14	&0	&0	&8	&1	&0\\ \hline
triangle	&0	&0	&7	&0	&1	&0	&0	&89	&0	&0	&12	&4	&0\\ \hline
cube	&0	&0	&0	&0	&0	&0	&0	&0	&147	&0	&0	&0	&0\\ \hline
cylinder	&0	&0	&0	&6	&2	&8	&16	&0	&4	&156	&1	&10	&0\\ \hline
parallelogram	&0	&0	&4	&0	&0	&0	&0	&0	&0	&0	&91	&0	&0\\ \hline
moon	&0	&3	&3	&2	&17	&0	&9	&17	&0	&0	&2	&133	&11\\ \hline
callout	&1	&34	&0	&22	&21	&22	&16	&25	&0	&0	&0	&0	&143\\ \hline
		\end{tabular}
			}
 		%\end{tabular}
 	%}
	\caption{Confusion Matrix}
	\label{tab:ConfusionMatrix}
	%\end{minipage}
\end{table*}

@@

\begin{figure}
	\centering
		\includegraphics[scale=0.1]{paperImages/LDsymbols.jpg.eps}
	\caption{Symbols Comparison on EL-DB symbols}.  %The graph shows the recognition rate of each symbol using different algorithms. 
	\label{fig:ELtest2}
\end{figure}

@@

 \begin{figure}
	\centering
		\includegraphics[scale=0.5]{paperImages/featuresdifference.jpg.eps}
	\caption{Feature Comparison on EL-DB} The effect of different features on accuracy.  %The graph shows the recognition rate of each symbol using different algorithms. 
	\label{fig:testFeaturesAll}
\end{figure}

 The main features affected by the segmentation stage are the geometric features computed in\textbf{FS1}. Hence those are the features we used to estimate the efficiency of the segmentation algorithm. The recognition accuracy using only the geometrical features is reported in Figure \ref{fig:testFeatonly} . The figure shows that \textsl{AlgS2} achieve better results.  %effect of the segmentation algorithm 
 %Figure \ref{fig:SampleSeg} shows a sample of the output of the segmentation block. The result of segmentation block is tested by their effect on the final recognition results using the features that will be highly affected using different algorithms like \textbf{FS1} and \textbf{FS4} (Section\ref{sec:Recognition}). Figure \ref{fig:testFeatonly} shows the result of the different algorithms using only \textbf{FS1 }features. 
 \begin{figure}
	\centering
		\includegraphics[scale=0.4]{paperImages/featureFS1only.jpg.eps}
	\caption{The effect of segmentation on Hs-DB accuracy} %The effect of symbol complexity.  %The graph shows the recognition rate of each symbol using different algorithms. 
	\label{fig:testFeatonly}
\end{figure}  
 \begin{figure}
	\centering
		\includegraphics[scale=0.4]{paperImages/featureFS1only.jpg.eps}
	\caption{The effect of segmentation on LD-DB accuracy} %The effect of symbol complexity.  %The graph shows the recognition rate of each symbol using different algorithms. 
	\label{fig:LDtestFeatonly}
\end{figure}  
 \begin{figure}
	\centering
		\includegraphics[scale=0.4]{paperImages/featureFS1only.jpg.eps}
	\caption{The effect of segmentation on EL-DB accuracy} %The effect of symbol complexity.  %The graph shows the recognition rate of each symbol using different algorithms. 
	\label{fig:ELtestFeatonly}
\end{figure}  
%
% \begin{figure}
%	\centering
%		\includegraphics[scale=0.5]{results/testFeat.eps}
%	\caption{Feature Comparison} The effect of different features on accuracy on \textsl{Hs-DB}.  %The graph shows the recognition rate of each symbol using different algorithms. 
%	\label{fig:testFeaturesAllHS}
%\end{figure}  
%
% \begin{figure}
%	\centering
%		\includegraphics[scale=0.5]{results/testF1.eps}
%	\caption{Feature Comparison} The effect of different features on accuracy on \textsl{MD-DB}.  %The graph shows the recognition rate of each symbol using different algorithms. 
%	\label{fig:testFeaturesAllMD}
%\end{figure}

@@

The result illustrated in this chapter shows the work done on the system and experiments performed. We showed result of three different dataset. The system performed better than most known algorithm on the EL-DB and LD-DB. This is due to the focus on structure and stroke based properties gained from the system after correctly segmenting the input strokes. The result also showed that even using \textsl{AlgS2} only as the segmentation algorithm the system perform better than other segmentation algorithm. Using different databases shows that the more the structure differences in the symbols the better recognition rate. LD-DB proved to have the lowest recognition rate due to the high similarity between its symbols.    % better than

>>>>

\chapter{Evaluation}
\label{sec:Evaluation}
This chapter describes and illustrates the experiments performed on the system. In the chapter, Section \ref{sec:Datasets} describes the datasets used. Section \ref{sec:ResultsDetails} demonstrates and analyzes the results.

The system has two main parts the DPSO stroke segmentation and symbol recognition. Each part is evaluated separately. The preprocessing procedures and computation is evaluated using their effect on the segmentation algorithm. These results are reported in section \ref{sec:ResultsDetails}. The effect of number of particles, the error thresholds and various other PSO parameters are investigated in Section \ref{sec:PSO}. %The results presented in Section \ref{sec:ResultsDetails} and \ref{sec:PSO}.

The recognition system evaluation is presented in Section \ref{sec:SegmentationAlgorithms}. The recognition rate (computed as the number of correctly recognized samples divided by the total number of samples in the test) for each segmentation algorithm compared to another segmentation algorithm are reported in \ref{sec:RecognitionAlgorithms}. Next, a comparison between different shapes and datasets and it influence on the recognition rate is presented in Section \ref{sec:EffectsofSymbolComplixity}. Finally, a comparison between different feature vectors is reported in Section \ref{sec:featuresComparisions}.

@@

 %We divided the dataset equally into training set and test set.  The results displayed are the recognition accuracy resulted from the classifier after recognizing the symbols. \\
%We divided the dataset into four sets each set contains four different users. Furthermore, each set is divided into train and test set where the trained set where used to train the classifiers and the test set where used for testing.  The algorithms are then tested using the four sets and the results are averaged.
\begin{figure}[]\centering
\fbox{  \parbox{8cm}{% 
		\includegraphics[scale=0.7]{images/symbolSet.eps}	}
		}
	\caption[Hs-DB Symbol Set]{The symboles Set in \cite{HeloiseBeautification} } 
	\label{fig:symbolSet}
\end{figure}

@@

	\caption[Symbols in LD-DB]{Example of Logic Symbols}
	\label{fig:LogicSet}
\end{figure}
\begin{figure}[]\centering

@@

	\caption[Symbols in EL-DB]{Example of Electrical Symbols}
	\label{fig:ElectSet}
\end{figure}
\begin{table}
\begin{center}
\scalebox{0.9}{
 \begin{tabular}{|p{5cm}|p{2.5cm}|p{2.5cm}|p{2.5cm}|}
 \hline
 & Hs-DB &  EL-DB & LD-DB \\ \hline
No of samples  &  7791 & 2764 & 1859 \\ \hline
No of categories  & 13 & 15 & 8 \\ \hline
Avg. Samples per Category& 600 & 184 & 232 \\\hline 
No of users  & 16 & 7 & 7 \\  \hline
Balanced & Yes&No & No \\ \hline
Splits  & 5 random splits  & 5 random splits  & 5 random splits  \\ \hline
Examples & Figure \ref{fig:symbolSet}  & Figure \ref{fig:ElectSet}  & Figure \ref{fig:LogicSet}   \\ \hline
\end{tabular}
}
\caption[Datasets Comparisons]{Datasets Comparisons} 
\label{tab:datasets}

@@

	\item [Recognition accuracy] We measure recognition performance for each algorithm by determining the number of correctly identified symbols in the whole dataset. Note that All the results are shown as the average of the five split of the dataset used. 
\end{description}

@@

 The effect of number of particles, the error thresholds and various other parameters was investigated. The result of these tests are shown in Figure \ref{fig:swarmtesting} and \ref{fig:swarmtesting2}. Figure \ref{fig:swarmtesting} shows that as the number of particles increase the \textit{Segmentation Error} value decrease. Similar results for the maximum swarm iterations are shown in Figure \ref{fig:swarmtesting}.  Other algorithm parameters like $c_1$,$c_2$ that were mentioned in Section\ref{sec:ParticleSwarmAlgorithm} are tested using similar tests (Figure \ref{fig:swarmparamterw.jpg} and \ref{fig:swarmtesting2}). The final values are for maximum number of iteration = 80 with 15 particles. The final number of particles and maximum swarm iteration used in the system was based trade off between errors achieved versus the computation time.

 \begin{figure}
	\centering		
	 \includegraphics[scale=0.5]{paperImages/swarmAgentTest.jpg.eps}
	 	\caption{Segmentation Error Vs. Number of particles}
	 	\label{fig:swarmtesting}
	%\caption{Experiments results :} a)    b) c) 
\end{figure}

@@

\begin{figure}
	\centering
		\includegraphics[scale=0.6]{results/LDRes.eps}
	\caption{Result Algorithms on LD-DB}
	\label{fig:LDRes}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[scale=0.6]{results/ElRes.eps}
	\caption{Results of Algorithms on EL-DB}
	\label{fig:ElRes}
\end{figure}

@@

 The effects of symbol complexity in a dataset were testing in the following experiment. These experiments test how many samples will be required to finally obtain good performance from the recognizer system. In the following experiments, we tested the system using different number of sample per category. 
 Figure \ref{fig:Alg1Ds} and \ref{fig:Alg2Ds} shows that Hs-DB requires more number of sample for training to achieve same result as in other data sets. This is due that it contains less signal and conceptual variation that the other two datasets. Figure \ref{fig:samplesofHS-DB.jpg} shows sample of data collected from one user in Hs-Db it is clear that it has reasonable amount of variation between users but it is limited. Recognizing symbols that contains high variation in drawing style using fewer symbols in training prove the efficiency of our system.
 \begin{figure}
	\centering
		\includegraphics{results/Alg1Ds.eps}
	\caption{AlgS1 on different datasets}
	\label{fig:Alg1Ds}
\end{figure}
\begin{figure}
	\centering
		\includegraphics{results/Alg2Ds.eps}
	\caption{AlgS2 on different Datasets }
	\label{fig:Alg2Ds}
\end{figure}
 \begin{figure}
	\centering
	\includegraphics[scale=0.5]{results/samplesofHS-DB.jpg.eps}
	\caption{Hs-DB shapes drawn by single user}
	\label{fig:samplesofHS-DB.jpg}
\end{figure}
  Figure \ref{fig:correct2.jpg} shows examples of correctly recognized symbol using our system. The figure shows that system recognized some hard to recognize example in both EL-DB and DL-DB. An example of symbols that was not correctly recognized are in Figure \ref{fig:erros}. Most of the wrong classifications were due to how messy the user draw symbols and how similarly they are conceptual.  Table \ref{tab:ConfusionMatrix} (confusion matrix) shows the types of error in Hs-DB which shows that the system was confused between parallelogram and trapezoid, moon and arch. Those errors were due to users drawing styles as some user may draw a parallelogram as a trapezoid.

  %55Table \ref{} show the confusion matrix of EL-DB which shows that most error were between capacitor, batter and crystal which differ only on number of parallel lines. 
\begin{figure}
	\centering
		\includegraphics{results/erros.jpg.eps}
	\caption{Error in Recognition }
	\label{fig:erros}
\end{figure}
\begin{figure}
	\centering
		\includegraphics{results/correct2.jpg.eps}
	\caption{Symbols Correctly Recognized}
	\label{fig:correct2.jpg}
\end{figure}

 \begin{table*}
	\centering
	%\small
%	\scalebox{0.7}{
		%	\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}\hline 
	\scalebox{0.7}{
		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}\hline 
 Categories 	&ellipse	&heart	&trapezoid	&pentagon	&arch	&hexagon	&square	&triangle	&cube	&cylinder	&parallelogram	&moon	&callout\\ \hline
ellipse	&155	&9	&0	&0	&0	&5	&0	&0	&0	&0	&0	&6	&0\\ \hline
heart	&0	&109	&1	&1	&25	&0	&0	&1	&0	&0	&2	&1	&1\\ \hline
trapezoid	&0	&0	&103	&5	&2	&0	&0	&2	&0	&0	&34	&0	&0\\ \hline
pentagon	&0	&0	&20	&121	&0	&20	&6	&2	&0	&0	&1	&0	&0\\ \hline
arch	&0	&1	&13	&0	&86	&0	&0	&2	&3	&0	&2	&0	&0\\ \hline
hexagon	&0	&0	&0	&0	&0	&98	&0	&0	&0	&0	&0	&0	&0\\ \hline
square	&0	&0	&1	&0	&2	&0	&107	&14	&0	&0	&8	&1	&0\\ \hline
triangle	&0	&0	&7	&0	&1	&0	&0	&89	&0	&0	&12	&4	&0\\ \hline
cube	&0	&0	&0	&0	&0	&0	&0	&0	&147	&0	&0	&0	&0\\ \hline
cylinder	&0	&0	&0	&6	&2	&8	&16	&0	&4	&156	&1	&10	&0\\ \hline
parallelogram	&0	&0	&4	&0	&0	&0	&0	&0	&0	&0	&91	&0	&0\\ \hline
moon	&0	&3	&3	&2	&17	&0	&9	&17	&0	&0	&2	&133	&11\\ \hline
callout	&1	&34	&0	&22	&21	&22	&16	&25	&0	&0	&0	&0	&143\\ \hline
		\end{tabular}
			}
 		%\end{tabular}
 	%}
	\caption{Confusion Matrix}
	\label{tab:ConfusionMatrix}
	%\end{minipage}
\end{table*}

@@

\begin{figure}
	\centering
		\includegraphics[scale=0.5]{results/ELSymbols.eps}
	\caption{Symbols Comparison on EL-DB symbols}.  %The graph shows the recognition rate of each symbol using different algorithms. 
	\label{fig:ELtest2}
\end{figure}

@@

 \begin{figure}
	\centering
		\includegraphics[scale=0.5]{results/FeatEL.eps}
	\caption{Feature Comparison on EL-DB} The effect of different features on accuracy.  %The graph shows the recognition rate of each symbol using different algorithms. 
	\label{fig:testFeaturesAll}
\end{figure}

 The main features affected by the segmentation stage are the geometric features computed in\textbf{FS1}. Hence those are the features we used to estimate the efficiency of the segmentation algorithm. The recognition accuracy using only the geometrical features is reported in Figure \ref{fig:testFeatonly} . The figure shows that \textsl{AlgS2} achieve better results.  %effect of the segmentation algorithm 
 %Figure \ref{fig:SampleSeg} shows a sample of the output of the segmentation block. The result of segmentation block is tested by their effect on the final recognition results using the features that will be highly affected using different algorithms like \textbf{FS1} and \textbf{FS4} (Section\ref{sec:Recognition}). Figure \ref{fig:testFeatonly} shows the result of the different algorithms using only \textbf{FS1 }features. 
 \begin{figure}
	\centering
		\includegraphics[scale=0.4]{paperImages/featureFS1only.jpg.eps}
	\caption{The effect of segmentation on Hs-DB accuracy} %The effect of symbol complexity.  %The graph shows the recognition rate of each symbol using different algorithms. 
	\label{fig:testFeatonly}
\end{figure}  
 \begin{figure}
	\centering
		\includegraphics[scale=0.3]{paperImages/featureFS1only.jpg.eps}
	\caption{The effect of segmentation on LD-DB accuracy} %The effect of symbol complexity.  %The graph shows the recognition rate of each symbol using different algorithms. 
	\label{fig:LDtestFeatonly}
\end{figure}  
 \begin{figure}
	\centering
		\includegraphics[scale=0.8]{results/F1EL.eps}
	\caption{The effect of segmentation on EL-DB accuracy} %The effect of symbol complexity.  %The graph shows the recognition rate of each symbol using different algorithms. 
	\label{fig:ELtestFeatonly}
\end{figure}  
%
% \begin{figure}
%	\centering
%		\includegraphics[scale=0.5]{results/testFeat.eps}
%	\caption{Feature Comparison} The effect of different features on accuracy on \textsl{Hs-DB}.  %The graph shows the recognition rate of each symbol using different algorithms. 
%	\label{fig:testFeaturesAllHS}
%\end{figure}  
%
% \begin{figure}
%	\centering
%		\includegraphics[scale=0.5]{results/testF1.eps}
%	\caption{Feature Comparison} The effect of different features on accuracy on \textsl{MD-DB}.  %The graph shows the recognition rate of each symbol using different algorithms. 
%	\label{fig:testFeaturesAllMD}
%\end{figure}

@@

The result illustrated in this chapter shows the work done on the system and experiments performed. We showed result of three different dataset. The system performed better than the benchmark algorithm on the EL-DB and LD-DB. This is due to the focus on structure and stroke based properties gained from the system after correctly segmenting the input strokes. The result also showed that even using \textsl{AlgS2} only as the segmentation algorithm the system perform better than other segmentation algorithms. Using different databases shows that the more the structure differences in the symbols the better recognition rate. LD-DB proved to have the lowest recognition rate due to the high similarity between its symbols.    % better than

### 2009-04-22 trunk/draft/chapterSurvey.tex
aftetr my change

\begin{figure}
	\centering
		\includegraphics[scale=0.7]{../../neededfiles/Figures/Overshootandundershoot.eps}
	\caption[Neat and Sloppy Symbols] {A sloppy and neat versions of symbol.}
	\label{fig:Overshootandundershoot}
\end{figure}

\begin{figure}
	\centering
		\includegraphics[scale=0.7]{../../neededfiles/Figures/overstroked.eps}
	\caption{Example of an over traced stroke}
	\label{fig:overstroked}
\end{figure}

@@

Arvo \cite{Fluid25} Tried to combine fast morphing and basic recognition for the sketch drawn as the user draw it. It tries to move the points of strokes drawn by the user draw into one of the known shapes (ex: box, lines and circle). It uses a relaxation and least square method for circles and uses the string of forces for finding best-fit box. However, their system can only identify circle and rectangles drawn using a single stroke.  
\begin{figure}
	\centering
	\subfigure[Feature area of line an arc]{
		\includegraphics{images/featurearearc.eps}}
		\subfigure[Feature area of line]{
				\includegraphics{images/featureareline.eps}}
	\caption{Feature Area}
	\label{fig:featurearearc}
\end{figure}

@@

\begin{figure}
	\centering
		\includegraphics[scale=0.7]{../../neededfiles/Figures/squarescematic.eps}
	\caption{Semantic Graph of a Square }
	\label{fig:squarescematic}
\end{figure}

@@

 Several visual grammar were introduced \cite{statisticalparsing26,Ladder30,GenericHMM28}. \cite{Ladder30,GenericHMM28}  Used visual description language which will generate the information of the structure and constrain of each object classified. The system automatically generates Java code for the recognizer for each object. The generated code cycles through the strokes drawn to check if any of the recognizers generated had interpreted any symbols partially or completely.  These systems are less computational expensive than graph matching approach but they also operate based on the output of the segmentation process. Any error in the segmentation process leads to huge error while parsing the whole sketch. Moreover, symbols cannot share strokes between them which influence and restrict how the user draws symbols. 
 % complexity of the graph matching problem 
\begin{figure}
	\centering
		\subfigure[An Arrow]
			{\label{fig:arrow1}\includegraphics[scale=0.75]{../../neededfiles/Figures/arrowladderdef1.eps}}
			\hfill
		\subfigure[Arrow grammar definition]
		 {\label{fig:arr2}\includegraphics[scale=0.88]{../../neededfiles/Figures/arrowladderdef2.eps}}
	\caption[Arrow Definition]{}
		\label{fig:arrowladderdef1}
\end{figure}

@@

In the third approach, the recognition focuses on appearance of shapes contrary to individual strokes or global shape properties. Kara \cite{imagetrainable48} used this approach while presenting a system that matches the input shape into a one of the prototypes in the database. Figure \ref{fig:template} shows an example of prototypes of some of the shapes in the system. Input shapes are first pose and scale normalized then four image similarity measures are used to match input shapes to the database prototypes. He used two measures (Hausdor distance) to measure similarity and two coefficients (Yule, Tanimoto) to measure dissimilarity. His approach allows the system to recognize a shape using only a single training sample as it is based on the shape prototype. However, the shape prototype must represent all transformation and variation the input shape can have. Moreover, they restrict the image representation to 48x48 pixels due to computational reasons. This restriction leads to eliminating some of the fine details that may be needed to distinguish some shape classes. There results on isolated symbols seem promising but the system has not been tested on full sketch that tends to have high overlapping between symbols. 
\begin{figure}
	\centering
		\includegraphics[scale=0.7]{images/template.eps}
	\caption{Prototypes of Shapes}
	\label{fig:template}
\end{figure}

@@

\section{Swarm Optimization Review}
\label{sec:ParticleSwramOptimizationReview}

%This seems to emerge of what is called 'collective intelligence' from often large simple agents.  
% start with swarm in general  .. say about flock , ant and usin in image processing 
% then speeak about PSO and  its firstly generated   (see article)
%mention that is best than ga (see thesis)

>>>>

\begin{figure}
	\centering
		\includegraphics[scale=0.7]{../../neededfiles/Figures/Overshootandundershoot.eps}
	\caption[Neat and Sloppy Symbols] {A sloppy and neat versions of symbol \cite{threeproblmes23}.}
	\label{fig:Overshootandundershoot}
\end{figure}

\begin{figure}
	\centering
		\includegraphics[scale=0.7]{../../neededfiles/Figures/overstroked.eps}
	\caption[Example of an over traced stroke]{Example of an over traced stroke \cite{overtraced24}}
	\label{fig:overstroked}
\end{figure}

@@

Arvo \cite{Fluid25} Tried to combine fast morphing and basic recognition for the sketch drawn as the user draw it. It tries to move the points of strokes drawn by the user draw into one of the known shapes (ex: box, lines and circle). It uses a relaxation and least square method for circles and uses the string of forces for finding best-fit box. However, their system can only identify circle and rectangles drawn using a single stroke.  
\begin{figure}
	\centering
	\subfigure[Feature area of line an arc]{
		\includegraphics{images/featurearearc.eps}}
		\subfigure[Feature area of line]{
				\includegraphics{images/featureareline.eps}}
	\caption[Feature Area]{Feature Area \cite{meanshift10}}
	\label{fig:featurearearc}
\end{figure}

@@

\begin{figure}
	\centering
		\includegraphics[scale=0.7]{../../neededfiles/Figures/squarescematic.eps}
	\caption[Semantic Graph of a Square ]{Semantic Graph of a Square \cite{mulitstroke5}}
	\label{fig:squarescematic}
\end{figure}

@@

 Several visual grammar were introduced \cite{statisticalparsing26,Ladder30,GenericHMM28}. \cite{Ladder30,GenericHMM28}  Used visual description language which will generate the information of the structure and constrain of each object classified. The system automatically generates Java code for the recognizer for each object. The generated code cycles through the strokes drawn to check if any of the recognizers generated had interpreted any symbols partially or completely.  These systems are less computational expensive than graph matching approach but they also operate based on the output of the segmentation process. Any error in the segmentation process leads to huge error while parsing the whole sketch. Moreover, symbols cannot share strokes between them which influence and restrict how the user draws symbols. 
 % complexity of the graph matching problem 
\begin{figure}
	\centering
		\subfigure[An Arrow]
			{\label{fig:arrow1}\includegraphics[scale=0.75]{../../neededfiles/Figures/arrowladderdef1.eps}}
			\hfill
		\subfigure[Arrow grammar definition]%{\cite{Ladder30}}
		 {\label{fig:arr2}\includegraphics[scale=0.88]{../../neededfiles/Figures/arrowladderdef2.eps}}
	\caption[Arrow Definition]{\cite{Ladder30}}
		\label{fig:arrowladderdef1}
\end{figure}

@@

In the third approach, the recognition focuses on appearance of shapes contrary to individual strokes or global shape properties. Kara \cite{imagetrainable48} used this approach while presenting a system that matches the input shape into a one of the prototypes in the database. Figure \ref{fig:template} shows an example of prototypes of some of the shapes in the system. Input shapes are first pose and scale normalized then four image similarity measures are used to match input shapes to the database prototypes. He used two measures (Hausdor distance) to measure similarity and two coefficients (Yule, Tanimoto) to measure dissimilarity. His approach allows the system to recognize a shape using only a single training sample as it is based on the shape prototype. However, the shape prototype must represent all transformation and variation the input shape can have. Moreover, they restrict the image representation to 48x48 pixels due to computational reasons. This restriction leads to eliminating some of the fine details that may be needed to distinguish some shape classes. There results on isolated symbols seem promising but the system has not been tested on full sketch that tends to have high overlapping between symbols. 
\begin{figure}
	\centering
		\includegraphics[scale=0.7]{images/template.eps}
	\caption[Prototypes of Shapes]{Prototypes of Shapes \cite{imagetrainable48}}
	\label{fig:template}
\end{figure}

@@

\section{Swarm Optimization Review}
\label{sec:ParticleSwramOptimizationReview}
%This seems to emerge of what is called 'collective intelligence' from often large simple agents.  
% start with swarm in general  .. say about flock , ant and usin in image processing 
% then speeak about PSO and  its firstly generated   (see article)
%mention that is best than ga (see thesis)
